### 2024-08-04 basic-statistics.qmd
20240803 - fixes

where $SS_{\text{effect}}$ is the sum of squares for the effect of interest and SS_{\text{total}} is the total sum of squares.

@@

where $SS_{\text{effect}}$ is the sum of squares for the effect of interest and SS_{\text{error}} is the sum of squares for the residual error term.

>>>>

where $SS_{\text{effect}}$ is the sum of squares for the effect of interest and $SS_{\text{total}}$ is the total sum of squares.

@@

where $SS_{\text{effect}}$ is the sum of squares for the effect of interest and $SS_{\text{error}}$ is the sum of squares for the residual error term.
